Methods

### 2024-02-02 methods.qmd
Re-organise metrics and remove metrics

@@

>>>>

Variation in age groups for different ethnicities:

<https://www.ethnicity-facts-figures.service.gov.uk/uk-population-by-ethnicity/demographics/age-groups/latest/>

<https://www.ethnicity-facts-figures.service.gov.uk/uk-population-by-ethnicity/demographics/age-groups/latest/#download-the-data>

@@

## Disparity

<https://www.health.state.mn.us/data/mchs/pubs/raceethn/rankingbyratio20032007.pdf>
